%-------------------------
% Google FDE GenAI resume (Kaustabh Ganguly)
% v5: added new work (12M translation, EmbeddingGemma deep fine-tune,
% production ML tuning, team enablement). Humanized prose preserved.
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage[colorlinks=true,urlcolor=accent,linkcolor=accent]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[default]{lato}
\usepackage{lastpage}
\usepackage{needspace}
\usepackage[left=0.4in,right=0.4in,top=0.3in,bottom=0.4in]{geometry}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\small\color{black!40} Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\definecolor{accent}{RGB}{0,51,102}

\titleformat{\section}
  {\vspace{2pt}\scshape\raggedright\large\color{accent}}
  {}{0em}{}
  [{\color{accent}\titlerule[1.2pt]}\vspace{-4pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \textbf{#1} \textbar\ #2 \\
    \textit{#3} \textbar\ \textit{#4}
  \vspace{-5pt}
}
\newcommand{\resumeProjectHeading}[2]{\item\small #1 #2\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%---------- HEADING ----------
\begin{flushleft}
  \textbf{\Huge \scshape \color{accent}Kaustabh Ganguly}\\[0.25em]
  \normalsize \textbf{Senior AI/ML Engineer \,|\, Production GenAI, Multi-Agent Systems \& MCP}\\[0.3em]
  \small Bangalore, India \textbar\ +91-8621063804 \textbar\ \href{mailto:kaustabhganguly@gmail.com}{kaustabhganguly@gmail.com}\\[0.15em]
  \footnotesize \href{https://scholar.google.com/citations?user=3AG6T5QAAAAJ}{Google Scholar} \textbar\ \href{https://github.com/stabgan}{github.com/stabgan} \textbar\ \href{https://www.npmjs.com/~stabgan}{npmjs.com/\textasciitilde stabgan} \textbar\ \href{https://huggingface.co/stabgan}{huggingface.co/stabgan} \textbar\ \href{https://linkedin.com/in/stabgan}{linkedin.com/in/stabgan} \textbar\ \href{https://stabgan.github.io}{stabgan.github.io}
\end{flushleft}
\vspace{-2pt}
{\color{accent}\hrule height 0.8pt}
\vspace{-4pt}

%----------- SUMMARY -----------
\section{Professional Summary}
\small
Senior engineer, five years in, building production GenAI that has to hold up inside real enterprise environments. At Gracenote (Nielsen) I run a \textbf{LangGraph} multi-agent workflow that lifted editorial no-touch approval from \textbf{30\% to 40\%}, led a DeepEval-gated migration from Claude 3.7 Sonnet to 4.5 Haiku (p95 latency halved, cost per request down 3x on a 10K-req/day service), and translated \textbf{12M multilingual catalog rows} through vLLM + FP8 at a total cost of about \textbf{\$460}. I have two MCP servers published on npm so other engineers can skip the OAuth and SSRF plumbing I had to work through, plus 8 fine-tuned Gemma 3 checkpoints on HuggingFace for clinical NLP. Before Gracenote I spent two years embedded with Johnson \& Johnson MedTech teams across North America and Asia, shipping an AUROC 0.95 contract-approval model inside their existing AWS (EC2 + Redshift + RDS) perimeter, no new infra. M.Tech from IIT Madras (clinical ML on MIMIC-IV), done alongside the day job.

%----------- PROFESSIONAL EXPERIENCE -----------
\section{Professional Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Gracenote, a Nielsen Company}{2025 -- Present}
    {Member of Technical Staff II (Senior AI/ML Engineer)}{Bangalore, India}
    \resumeItemListStart
      \resumeItem{Built a \textbf{LangGraph} supervisor/specialist workflow with stateful checkpointing and HITL interrupts; a small DSPy module (over BootstrapFewShot) mines editorial rules from live production traces and the workflow applies them to incoming metadata. Editorial no-touch approval rose from \textbf{30\% to 40\%}.}
      \resumeItem{Owned the Claude 3.7 Sonnet to 4.5 Haiku cutover on the 10K-req/day media-description path. Wrote the DeepEval regression suite, ran it as a canary gate, and kept task quality within one point of baseline on the golden set. \textbf{p95 latency fell 50\%, cost per request dropped 3x}; two adjacent teams picked up the same pattern.}
      \resumeItem{Compiled the translator prompt with DSPy MIPROv2 over 300 diversity-sampled exemplars drawn from a 10K pool; optimizer token spend fell about \textbf{30x per trial}, which freed budget for 3x more trials at the same spend.}
      \resumeItem{Then ran it at scale: translated \textbf{\textasciitilde 12M multilingual catalog rows} through a Gemma 3 27B model on \textbf{4$\times$ L40S GPUs with vLLM and FP8 quantization} (hardware-supported on L40S). fastText gated language detection up front so only non-English rows were sent through. Total spend: \textbf{\textasciitilde \$460} for the full 12M-row job; the output now feeds several downstream systems. Golden eval references were generated locally via an Ollama + Gemma 3 4B teacher loop, \textbf{$\geq$95\%} accepted by reviewers on an $N{=}500$ spot-check.}
      \resumeItem{Tightened a production classification model that had been limping along: proper hyperparameter search plus a swap from XGBoost to LightGBM brought single-entry inference \textbf{2x faster} and cut false positives by \textbf{58\%}.}
      \resumeItem{Took over the Netflix and Amazon catalog ingestion pipeline (\textbf{1.5M records/month}). Temporal heuristics hit 97\% precision and knocked false positives down \textbf{40\%} against the prior rules-only baseline; partner-data escalations eased off with it.}
      \resumeItem{Deep fine-tune of \textbf{EmbeddingGemma 300M} as a retrieval bi-encoder. Trained on a p4de EC2 box (8$\times$ A100 80GB) with \textbf{DeepSpeed ZeRO}, Unsloth, mixed-precision, and all 8 GPUs doing evaluation in parallel. Technique stack: curriculum hard-negative mining, a 4-directional GTE-style contrastive loss, learning-rate annealing, and \textbf{Matryoshka representation learning with weighted dimension slices}. I drove technique selection through an AutoResearch harness I built over MCP servers that scouts relevant literature before each experiment. \textbf{Accuracy@1 and accuracy@5 each improved by 12 points} on a temporally-split holdout. {\itshape CTO recognition for the LangGraph work and the Haiku migration.}}
    \resumeItemListEnd

  \resumeSubheading
    {Tata Consultancy Services (Client: Johnson \& Johnson MedTech)}{2023 -- 2025}
    {Data Architect \& Data Scientist, Contract Commitment Portal}{Kolkata, IN / Remote}
    \resumeItemListStart
      \resumeItem{Embedded across NA and APAC for discovery on the Contract Commitment Portal ML rollout. Working with approval-workflow owners, Finance leads, and the program Director, I translated an undocumented manual-review heuristic into a scoped ML spec that cleared legal, security, and the change-advisory board inside a regulated medical-device business.}
      \resumeItem{Shipped the analyst decision-support model for contract approvals: LightGBM, isotonic-calibrated, temporal holdout with a leakage audit. Full coverage across NA/APAC cases. \textbf{AUROC 0.95}, 4--5 hours saved per case, approval cycle cut \textbf{2x}. It all ran on the customer's existing AWS footprint; no new infra, no new vendor paperwork.}
      \resumeItem{Set up production MLOps around it: daily drift alerts, automated isotonic recalibration every two days, and a 2-month A/B pilot that didn't have to roll back. The model is now the default decision path on the portal.}
      \resumeItem{Built a LangChain \textit{Tableau Q\&A} bot as a PoC so analysts could hit dashboards conversationally, an early agentic-RAG experiment inside an enterprise setting.}
      \resumeItem{Architected On-Demand-Refresh (one-click ad-hoc ETL for 10 analysts: 3 hours down to minutes) and a Fail-Proof-Mechanism (Excel to Parquet with dynamic Redshift DDL). Schema-break incidents came down from \textasciitilde 15/month to \textasciitilde 2/month.}
    \resumeItemListEnd

  \needspace{6\baselineskip}
  \resumeSubheading
    {Tata Consultancy Services (J\&J COE R\&D)}{2022 -- 2023}
    {Software Engineer, Data Platform (POCs \& Automation)}{India}
    \resumeItemListStart
      \resumeItem{Prototyped a transformer-based clinical-text extractor (BERT-family, HuggingFace) over de-identified J\&J records with a distributed team across three regions; the PoC seeded the CCP ML workstream I later led.}
      \resumeItem{Shipped \textbf{Data Sentry} inside J\&J's multi-cloud estate (AWS, Azure, GCP), using \textbf{Microsoft Graph OAuth 2.0} after shadowing the IAM team. Onboard/offboard for about 500 users went from days to minutes.}
    \resumeItemListEnd

  \resumeSubheading
    {Tata Consultancy Services (J\&J Vision)}{2020 -- 2022}
    {Software Engineer, Data Platform (Data Engineer to Lead)}{India}
    \resumeItemListStart
      \resumeItem{\textbf{Promoted IC to Lead in 18 months.} Ran production ETL on AWS (Control-M): \textasciitilde 50\,GB/day across 40 daily jobs feeding ML and analytics worldwide. Tuned Redshift views to \textasciitilde 3x faster on the hot paths.}
      \resumeItem{SDET across 20+ SIT cycles with minimal rework, owned 100+ production releases, led a team of 10+ engineers.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- OPEN SOURCE -----------
\needspace{5\baselineskip}
\section{Open Source \& MCP Ecosystem}
\begin{itemize}[leftmargin=0.15in, label={}]
\small
\item \textbf{\href{https://www.npmjs.com/package/@stabgan/openrouter-mcp-multimodal}{@stabgan/openrouter-mcp-multimodal}} (TypeScript, MCP, Docker). Production MCP server fronting 300+ LLMs with native vision, image generation, and tool-calling. URL fetch is bounded and SSRF-safe (blocks private, link-local, and reserved IPs); sharp handles image optimization; npm trusted-publishing runs over GitHub Actions OIDC so there are no long-lived tokens in the repo.
\item \textbf{\href{https://www.npmjs.com/package/@stabgan/steelmind-mcp}{@stabgan/steelmind-mcp}} (TypeScript, MCP). Structured-thinking plus steel-manning verification for AI agents (Socratic self-questioning, dialectical evaluation; MetaCrit, arXiv 2507.15015). 90 automated tests, stdio transport, drop-in with Claude Desktop, Cursor, and other MCP clients.
\item \textbf{\href{https://github.com/stabgan/mcp-icd10}{mcp-icd10}} (Python, MCP). Offline MCP server for ICD-10-CM, ICD-9-CM, and WHO ICD-10 lookup with GEMs crosswalk: 124K codes, 102K mappings, no API keys, no network calls. Built this after I kept wanting an MCP tool that worked inside regulated environments.
\item \textbf{AutoResearch MCP harness} (internal). Custom harness I wrote around MCP servers that scouts relevant literature and benchmarks before each experiment; drove the technique picks on the EmbeddingGemma fine-tune above. Team-facing MCP utilities and agent harnesses built alongside to speed up routine research and eval work.
\item \textbf{HuggingFace} (\href{https://huggingface.co/stabgan}{huggingface.co/stabgan}). 8 fine-tuned Gemma 3 1B checkpoints for clinical NLP and 15 curated datasets (PubMed, ICD-10 benchmarks).
\item \textbf{\href{https://github.com/stabgan/awesome-loss-functions}{awesome-loss-functions}}. A collection I maintain of 350+ loss functions across 25+ AI subdomains with papers, math, and implementations.
\end{itemize}

%----------- TECHNICAL SKILLS -----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in]
  \item \small \textbf{Agentic \& Multi-Agent:} LangGraph (supervisor/subgraphs, checkpointers, HITL interrupts), LangChain, DSPy (Signatures, MIPROv2, BootstrapFewShot), CrewAI, Google Agent Development Kit (ADK); ReAct, self-reflection, and hierarchical delegation patterns.
  \item \small \textbf{MCP \& Integration:} Model Context Protocol server development (stdio, Docker), tool-calling, function-calling, OAuth 2.0, Microsoft Graph, SSRF-safe URL fetching, scope minimization, tool-poisoning awareness.
  \item \small \textbf{LLM Evaluation \& Observability:} DeepEval regression suites, LLM-as-a-Judge, tokens/sec, cost per request, p95/p99 latency, granular tracing, prompt optimization (MIPROv2, greedy diversity selection), golden-set curation.
  \item \small \textbf{NLP, Embeddings \& LLMs:} Gemini (Vertex AI), Claude (Sonnet, Haiku), Gemma 3 (1B/4B/27B), Qwen, HuggingFace Transformers, Ollama, vLLM, FP8 quantization, LoRA/QLoRA (Unsloth), DeepSpeed ZeRO, bi-encoder / cross-encoder fine-tuning, curriculum learning, hard-negative mining, Matryoshka representation learning, 4-directional GTE-style loss, RAG, synthetic data generation, fastText.
  \item \small \textbf{ML \& Deep Learning:} PyTorch, TensorFlow, scikit-learn, LightGBM, XGBoost, CatBoost, Optuna, SHAP, Weights \& Biases, calibration, survival analysis (CoxPH, DeepSurv), ensembling.
  \item \small \textbf{Languages:} Python (primary, 5+ years in production), TypeScript, SQL, Go, Java, Bash, R.
  \item \small \textbf{Cloud \& Infrastructure:} Google Cloud (Vertex AI, Gemini API, BigQuery), AWS (S3, EC2 p4de/L40S, RDS, Lambda, Redshift, SageMaker, Bedrock), Azure, Docker, Kubernetes, Terraform, GitHub Actions (OIDC).
  \item \small \textbf{Data \& MLOps:} Redshift, PostgreSQL, Snowflake, Parquet, Airflow, Jenkins, CI/CD, A/B testing, drift detection, canary rollout, release management.
\end{itemize}

%----------- EDUCATION -----------
\needspace{11\baselineskip}
\section{Education}
\resumeSubHeadingListStart

  \resumeSubheading
    {Indian Institute of Technology Madras (IIT Madras)}{2023 -- 2025}
    {M.Tech, Industrial Artificial Intelligence (GPA: 8.66/10), done alongside full-time work}{Chennai, IN}
    \resumeItemListStart
      \resumeItem{\textbf{Thesis:} Machine Learning for Clinical Decision Support on MIMIC-IV. \textbf{Coursework:} ML, DL, Statistical Methods, Time Series, Optimization, NLP, Data Mining, OR.}
      \resumeItem{\textbf{Thesis P1:} Rare-disease ICD prediction. Ontology-based augmentation (ORDO to SNOMED CT); fine-tuned Gemma 3 and Qwen 3 on A100/H100 via 4-bit QLoRA with Unsloth; served locally via Ollama; tracked with W\&B.}
      \resumeItem{\textbf{Thesis P2:} SA-AKI mortality prediction. Optuna-tuned LightGBM (\textbf{AUROC 0.749}) with isotonic calibration and SHAP; CoxPH plus a custom PyTorch DeepSurv (C-index $\sim$0.69); positive net benefit on decision curve analysis.}
    \resumeItemListEnd

  \resumeSubheading
    {Kalyani Government Engineering College (KGEC)}{2016 -- 2020}
    {B.Tech, Information Technology (CGPA: 8.15/10)}{Kalyani, IN}
    \resumeItemListStart
      \resumeItem{5 peer-reviewed papers in IoT and fuzzy systems (Elsevier, IEEE, Springer); see Publications. Swami Vivekananda Merit-cum-Means Scholar (4-year government scholarship).}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- PUBLICATIONS -----------
\needspace{4\baselineskip}
\section{Publications}
\small
5 peer-reviewed papers (Elsevier, IEEE, Springer); lead paper has \textbf{22 citations}.
\begin{itemize}[leftmargin=0.15in, label={}]
\small
\item \textbf{[1]} PS Banerjee, A Karmakar, M Dhara, \textbf{K Ganguly}, S Sarkar. ``Predicting bradycardia and atrial fibrillation using fuzzy logic and IoT sensors.'' \textit{Medicine in Novel Technology and Devices} (Elsevier), 2021.
\item \textbf{[2]} A Karmakar, \textbf{K Ganguly}, P Ghosh, A Mazumder, PS Banerjee, D De. ``FemmeBand: IoT smart security band using EMG sensors.'' \textit{Innovations in Systems and Software Engineering} (Springer), 2024.
\item \textbf{[3]} \textbf{K Ganguly}, A Karmakar, PS Banerjee. ``ValveCare: fuzzy-based heart disease prediction with Arduino IoT.'' \textit{Int'l Conf.\ on Computational Intelligence} (Springer), 2021.
\item \textbf{[4]} A Karmakar, \textbf{K Ganguly}, PS Banerjee. ``SafeBand: IoT smart security band with instant SOS.'' \textit{Proc.\ ICACA} (Springer), 2021.
\item \textbf{[5]} A Karmakar, \textbf{K Ganguly}, PS Banerjee. ``HeartHealth: multi-attribute heart monitoring via fuzzy-TOPSIS.'' \textit{IEEE DevIC}, 2021.
\end{itemize}

%----------- PROJECTS -----------
\needspace{4\baselineskip}
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{ICD-10-CM Monographs at Scale on Vertex AI} $|$ \emph{Python, Gemini (Vertex AI), Multithreading, Flask}}{}
    \resumeItemListStart
      \resumeItem{Generated detailed disease monographs for \textasciitilde 70K ICD-10-CM codes in parallel on Google Vertex AI (28 prompts across 14 regions), then shipped an offline encyclopedia web app that medical coders now use daily.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Saaki, SA-AKI Mortality Prediction (OSS)} $|$ \emph{Python, CatBoost, XGBoost, LightGBM, MIMIC-IV}}{}
    \resumeItemListStart
      \resumeItem{Open-source ICU mortality prediction, extended from my M.Tech thesis. 356 clinical features from the first 24 hours of stay, CatBoost ensemble at \textbf{AUROC 0.80}, leakage-aware pipeline with stratified evaluation.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- CERTIFICATIONS -----------
\section{Certifications \& Training}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
Statistical Learning with Python (Stanford University, 2025) \textbar\ AWS-ML: Machine Learning Pipeline on AWS, 30-hr hands-on workshop (2024) \textbar\ PCAP, Certified Associate in Python Programming (2023)
}}
\end{itemize}

%----------- ACHIEVEMENTS -----------
\section{Achievements \& Honors}
\begin{itemize}[leftmargin=0.15in]
  \item \small GATE Statistics (ST) 2024: \textbf{AIR 410} (top \textasciitilde 1\%). TCS CodeVita 2019: \textbf{Rank 585 / 100K+} (top 0.6\%).
  \item \small Swami Vivekananda Merit-cum-Means Scholar (4-year government scholarship); Employee of the Month at TCS.
  \item \small Run monthly tech talks for the team on emerging tools; publish internal MCP servers to boost team productivity; mentored 25+ engineers across career.
\end{itemize}

%----------- RECOMMENDATIONS -----------
\section{Select Recommendations}
\begin{itemize}[leftmargin=0.15in]
  \item \small \textit{``Instrumental in designing and architecting the data and machine learning pipelines\,...\,which needed out of the box thinking.\,...\,His command over technology specially in data, machine learning and AI is really commendable. Any team would be lucky to have him.''} --- Joy Smith Saha, Data Visualization Consultant, TCS (direct manager)
  \item \small \textit{``Deep technical expertise, especially in Python, and his ability to translate complex requirements into elegant, efficient code.\,...\,He's the kind of engineer you can trust with critical tasks.''} --- Suranjana Ghosh, Technical Architect, TCS (direct manager)
\end{itemize}

\end{document}
